Supporting Information for ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test''

### 2024-06-16 manuscript/manuscript.tex
cleaning up of supplement

\newcommand{\jy}[1]{}
\newcommand{\eds}[1]{}
\newcommand{\mc}[1]{}

@@

Continuing using the notation in the independent case,
we use $F^{(b)}_n$ and $\hat\theta^{(b)}_n$ for the empirical distribution and
the estimated parameters based on the $b$th bootstrap sample,
$b = 1, \ldots, B$.
We then use block bootstrap to approximate the asymptotic distribution of
the KS statistic under $H_0$. In particular, we
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)])$
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x))$, and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n]))$ as
an approximation of the distribution of $\sqrt{n}(F(x; \theta_n) - F(x))$.
The expected values $E[F^{(b)}_n(x)]$ and
$E[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
$E[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
$E[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.

Then, we can define
\begin{align*}
  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)]) - 
             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n)]) \\
           &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
             \sqrt{n}(E[F^{(b)}_n(x)] - F(x; E[\hat\theta^{(b)}_n])),
\end{align*}
and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$. Each $T_n^{(b)}$,
$b =1, \ldots, B$, is considered a draw from a distribution that approximates
the distribution of $T_n$. Therefore, the p-value of the observed statistic
$T_n$ can be assessed by positioning it against the empirical distribution of
$T_n^{(b)}$, $b = 1, \ldots, B$.

In summary, the procedure of the NPBB test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Obtain parametrically fitted parameters 
  $\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) \Big\vert.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}
The p-value of the block bootstrap KS test can be approximated
as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.

\jy{Recover the definition of jy and eds for comments. Prepare two
  definitions in the source so that one can be easily commented out.}

@@

\jy{In the Supp: make sure notations are consistent (e.g., use
  $\{X_t: t = 1, \ldots, n\}$ for observed data);
  clean up the styles (linewidth etc.)}

@@

\begin{proposition}\label{prop:Tnboot}
  As $1/l+l/n\rightarrow 0$,
  \[
    \big\vert \mathbb{P}(T_n^*\leq x \mid \{X_t: t = 1, \ldots, n\}) -
    \mathbb{P}(T_n\leq x) \big\vert
    \overset{a.s.}{\rightarrow} 0
  \]
  for any fixed $x$, where and $T_n^*$ is the the statistic computed 
  based on the bootstrap sample $\{X_t^*: t = 1, \ldots, n\}$.
\end{proposition}

>>>>

\newcommand{\jy}[1]{\textcolor{blue}{JY: (#1)}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}

@@

Continuing using the notation in the independent case,
we use $F^{(b)}_n$ and $\hat\theta^{(b)}_n$ for the empirical distribution and
the estimated parameters based on the $b$th bootstrap sample,
$b = 1, \ldots, B$.
We then use block bootstrap to approximate the asymptotic distribution of
the KS statistic under $H_0$. In particular, we
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)])$
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x; \theta_0))$, and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]))$ as
an approximation of the distribution of 
$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$.
Here $\mathbb{E}^{(b)}$ denotes the expectation with respect to the bootstrap 
distribution 
(i.e., the randomness due
to the resampling using block bootstrap) conditional on the observations 
$X_1, \dots, X_n$.
The expected values $\mathbb{E}^{(b)}[F^{(b)}_n(x)]$ and
$\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
$\mathbb{E}^{(b)}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
$\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.

Then, we can define
\begin{align*}
  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)]) - 
             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n)]) \\
           &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
             \sqrt{n}(\mathbb{E}^{(b)}[F^{(b)}_n(x)] - F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n])),
\end{align*}
and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$. Each $T_n^{(b)}$,
$b =1, \ldots, B$, is considered a draw from a distribution that approximates
the distribution of $T_n$. Therefore, the p-value of the observed statistic
$T_n$ can be assessed by positioning it against the empirical distribution of
$T_n^{(b)}$, $b = 1, \ldots, B$.

In summary, the procedure of the NPBB test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Obtain parametrically fitted parameters 
  $\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) \Big\vert.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(\mathbb{E}^{(b)}[F^{(b)}_n(x)] - 
  F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}
The p-value of the block bootstrap KS test can be approximated
as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.

\jy{Recover the definition of jy and eds for comments. Prepare two
  definitions in the source so that one can be easily commented out.}
\mc{addressed}

@@

\jy{In the Supp: make sure notations are consistent (e.g., use
  $\{X_t: t = 1, \ldots, n\}$ for observed data);
  clean up the styles (linewidth etc.)}
\mc{addressed}

@@

\begin{proposition}\label{prop:Tnboot}
  As $1/l+l/n\rightarrow 0$,
  \[
    \big\vert \mathbb{P}(T_n^*\leq x \mid \{X_t: t = 1, \ldots, n\}) -
    \mathbb{P}(T_n\leq x) \big\vert
    \overset{a.s.}{\rightarrow} 0
  \]
  for any fixed $x$, where and $T_n^*$ is the the statistic computed 
  based on the bootstrap sample $\{X_t^{(b)}: t = 1, \ldots, n\}$.
\end{proposition}

### 2024-06-16 manuscript/supplement.tex
cleaning up of supplement

\begin{proof}[Proof of Proposition~1]
We first derive the limiting distribution of the KS statistic under the null. Suppose $\hat{\theta}_n$ admits the expansion:
\begin{align}\label{eq-expan}
\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i;\theta_0) + \frac{1}{\sqrt{n}}R_n,    
\end{align}
where $h(\cdot;\theta_0)$ is the influence function with $\mathbb{E}[h(X_i;\theta_0)]=0$ and $R_n$ is the remainder term satisfying that
$R_n\overset{p}{\rightarrow} 0.$ Write $G_n(x):=\sqrt{n}(F_n(x)-F(x))$ and let $f(x;\theta)=\partial F(x;\theta)/\partial \theta$. We assume $\theta \in \mathbb{R}$ for ease of presentation.

Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent time series, we have the joint convergence of 
$V_n:=(G_n(x_1),\dots,G_n(x_m),\sqrt{n}(\hat{\theta}_n-\theta_0))$
to some Gaussian limit, with the covariance matrix being $\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
%\begin{align*}
%\Sigma_{m+1}=\begin{pmatrix}
%df & df & \cdots & df\\   
%df & df & \cdots & df\\ 
%\cdots & \cdots & \ddots & \cdots  \\ 
%df & df & \cdots & df
%\end{pmatrix}    
%\end{align*} 
Moreover, we can show the tightness of the process $G_n(x)$. 
For sufficiently small $\delta$, and leveraging the properties of weakly 
dependent sequences, we can show that
\[ \sup_{|x - y| < \delta} |G_n(x) - G_n(y)| = \sup_{|x - y| < \delta} 
\sqrt{n}|(F_n(x) - F(x)) - (F_n(y) - F(y))| \]
is small with high probability.
Specifically, since $F(x)$ is continuous, for small 
$\delta$, $|F(x) - F(y)|$ is small. For the empirical 
distribution function $F_n(x)$, the increments $|F_n(x) - F_n(y)|$ are 
also controlled. 
This implies that the process $G_n(x)$ does not exhibit large oscillations over 
small intervals, thus satisfying the criterion for tightness.
Therefore, we have
\begin{align*}
\begin{pmatrix}
G_n(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n)-F(x;\theta_0))
\end{pmatrix}\Rightarrow
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align*}
jointly, where $G_{\infty}(x)$ is a Gaussian process with the covariance function defined as
\begin{align*}
\text{Cov}(G_{\infty}(x),G_{\infty}(x'))=& \lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(\mathbf{1}\{X_i\leq x\},\mathbf{1}\{X_j\leq x'\})
\\=& \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},\mathbf{1}\{X_0\leq x'\}),
\end{align*}
and $U\sim N(0,s^2)$ with 
\begin{align*}
s^2=\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),h(X_j;\theta_0))
= \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),h(X_0;\theta_0)),
\end{align*}
and the covariance between $U$ and $G_{\infty}(x)$ is given by
\begin{align*}
\text{Cov}(U,G_\infty(x))=&\lim_{n\rightarrow+\infty}
\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),\mathbf{1}\{X_j\leq x\})
\\=&\sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
\end{align*}
By the continuous mapping theorem, we obtain
\begin{align*}
T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|.    
\end{align*}

@@

Denote by $\mathbb{E}^*$, $\text{Var}^*$ and $\text{Cov}^*$
the expectation, variance and covariance conditional on $X_{1:n}$ in the bootstrap world. Assuming that $n=kl$ with $l$ being the block size and $k$ being the number of blocks, the bootstrap marginal distribution is 
\begin{align*}
\rho_n^*=\frac{1}{n}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j} \delta_{X_i},    
\end{align*}
where $\delta_x$ denotes a point mass at $x$, and $S_1,\dots,S_k$ are i.i.d uniform on $\{1,\dots,n-l+1\}$. 
Define $G_n^*(x)$ in the same way as $G_n(x)$ with $X_{1:n}$ being replaced by the bootstrap samples $X_{1:n}^*=\{X_1^*,\dots,X_n^*\}$.

\begin{proof}]Proof of Proposition~2]
    We want to show that
\begin{align}\label{eq-con-boot}
\begin{pmatrix}
G_n^*(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n^*)-F(x;\hat{\theta}_0))
\end{pmatrix}\Rightarrow^{*}
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align}
where $\Rightarrow^*$ means convergence in distribution almost surely and $\hat{\theta}_0:=\mathbb{E}^*[\hat{\theta}_n^*]$. 
In the bootstrap world, we have an expansion similar to (\ref{eq-expan}):
\begin{align*}
\hat{\theta}_n^*-\hat{\theta}_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i^*;\hat{\theta}_0) + \frac{1}{\sqrt{n}}R_n^*,    
\end{align*}
where $R_n^* \overset{p^*}{\rightarrow} 0$, where $\overset{p^*}{\rightarrow}$ means convergence in probability almost surely. Note that 
\begin{align*}
\mathbb{E}^*\left[\frac{1}{n}\sum^{n}_{i=1}h(X_i^*;\hat{\theta}_0)\right]
=&\frac{1}{n}\sum^{k}_{j=1}\mathbb{E}^*\left[\sum^{S_j+l-1}_{i=S_j}h(X_{i};\hat{\theta}_0)\right]
\\=&\frac{k}{n^2}[\sum^{n - l + 1}_{j=1}\sum^{j+l-1}_{i=j}h(X_{i};\hat{\theta}_0) +
\sum^{n}_{j=n - l + 2}[\sum^{n}_{i=j}h(X_{i};\hat{\theta}_0) +
\sum^{j - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)]]
\\=&\frac{k}{n^2}\sum^{n}_{i=1}l h(X_{i};\hat{\theta}_0),
\end{align*}.
Moreover, we have
\begin{align*}
\text{var}^*\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^*;\theta_0^*)\right)
=&\text{var}^*\left(\frac{1}{\sqrt{n}}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j}h(X_{i};\hat{\theta}_0)\right)
\\=&\frac{1}{l}\text{var}^*\left(\sum^{S_1+l-1}_{i=S_1}h(X_{i};\hat{\theta}_0)\right)
\\=&\frac{1}{ln}\sum^{n}_{t=1}(W_t-\bar{W})^2
\end{align*}
with $W_t=
 \begin{cases}
\sum^{t+l-1}_{i=t}h(X_i;\hat{\theta}_0)  & \text{if } t \leq n - 1 + 1,\\
\sum^{n}_{i=t}h(X_{i};\hat{\theta}_0) +
\sum^{t - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)  & \text{if } t \geq n - 1 + 2
\end{cases}$
and $\bar{W}=\sum^{n}_{t=1}W_t/n$,
which is expected to converge to $s^2$ almost surely. Similar calculations apply to $G_n^*(x)$ and we expect that
\begin{align*}
&\text{Cov}^*(G_n^*(x),G_n^*(x'))\overset{a.s.}{\rightarrow}   \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},\mathbf{1}\{X_0\leq x'\}),\\
&\text{Cov}^*\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^*;\hat{\theta}_0), G_n^*(x)\right)\overset{a.s.}{\rightarrow} \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
\end{align*}
By showing the finite-dimensional convergence and tightness in the bootstrap world (conditional on the data $X_{1:n}$), we can establish \eqref{eq-con-boot}.
From the CLT, the process $G_n^*(x) = \sqrt{n}(F_n^*(x) - F_n(x))$ converges 
to 
$G_{\infty}(x)$.

For $\sqrt{n}(F(x;\hat{\theta}_n^*) - F(x;\hat{\theta}_0))$, using the first-
order Taylor 
expansion around $\hat{\theta}_0$, we have:
\[
F(x;\hat{\theta}_n^*) \approx F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^* - \hat{\theta}_0),
\] so
\[
\sqrt{n}(F(x;\hat{\theta}_n^*) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
(F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^* - \hat{\theta}_0) - F(x;\hat{\theta}_0)) 
\approx
f(x; 
\hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^* - \hat{\theta}_0).
\].

Substituting the expansion of $\hat{\theta}_n^*$:
\[
\sqrt{n} (\hat{\theta}_n^* - \hat{\theta}_0) = \frac{1}{\sqrt{n}} \sum_{i=1}^{n} 
h(X_i^*; \hat{\theta}_0) + R_n^*.
\]

Since $R_n^* \overset{p^*}{\rightarrow} 0$, 
\[
\sqrt{n}(F(x;\hat{\theta}_n^*) - F(x;\hat{\theta}_0)) \approx 
f(x; \hat{\theta}_0) \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^*; 
\hat{\theta}_0) \right).
\]

The term $\frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^*; \hat{\theta}_0)$ 
converges in distribution to a normal random variable $U$ with variance 
$s^2$.
We can show tightness of $G_n^*(x)$ similarly to how we established 
tightness of $G_n(x)$
The results then follow from the continuous mapping theorem.
\end{proof}

%\bibliographystyle{plain} 
%\bibliography{ref}

>>>>

\begin{proof}[Proof of Proposition~1]
We first derive the limiting distribution of the KS statistic under the null. 
Suppose $\hat{\theta}_n$ admits the expansion:
\begin{align}\label{eq-expan}
\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{t=1}h(X_i;\theta_0) + 
\frac{1}{\sqrt{n}}R_n,    
\end{align}
where $h(\cdot;\theta_0)$ is the influence function with 
$\mathbb{E}[h(X_i;\theta_0)]=0$ and $R_n$ is the remainder term satisfying that
$R_n\overset{p}{\rightarrow} 0.$ Write $G_n(x):=\sqrt{n}(F_n(x) - 
F(x; \theta_0))$ 
and let $f(x;\theta)=\partial F(x;\theta)/\partial \theta$. We assume 
$\theta \in \mathbb{R}$ for ease of presentation.

Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent 
time series, we have the joint convergence of 
$V_n:=(G_n(x_1),\dots,G_n(x_m),\sqrt{n}(\hat{\theta}_n-\theta_0))$
to some Gaussian limit, with the covariance matrix being 
$\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
%\begin{align*}
%\Sigma_{m+1}=\begin{pmatrix}
%df & df & \cdots & df\\   
%df & df & \cdots & df\\ 
%\cdots & \cdots & \ddots & \cdots  \\ 
%df & df & \cdots & df
%\end{pmatrix}    
%\end{align*} 
Moreover, we can show the tightness of the process $G_n(x)$. 
For sufficiently small $\delta$, and leveraging the properties of weakly 
dependent sequences, we can show that
\[ \sup_{|x - y| < \delta} |G_n(x) - G_n(y)| = \sup_{|x - y| < \delta} 
\sqrt{n}|(F_n(x) - F(x)) - (F_n(y) - F(y))| \]
is small with high probability.
Specifically, since $F(x)$ is continuous, for small 
$\delta$, $|F(x) - F(y)|$ is small. For the empirical 
distribution function $F_n(x)$, the increments $|F_n(x) - F_n(y)|$ are 
also controlled. 
This implies that the process $G_n(x)$ does not exhibit large oscillations over 
small intervals, thus satisfying the criterion for tightness.
Therefore, we have
\begin{align*}
\begin{pmatrix}
G_n(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n)-F(x;\theta_0))
\end{pmatrix}\Rightarrow
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align*}
jointly, where $G_{\infty}(x)$ is a Gaussian process with the covariance 
function defined as
\begin{align*}
\text{Cov}(G_{\infty}(x),G_{\infty}(x'))=& 
\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}
\text{Cov}(\mathbf{1}\{X_i\leq x\},\mathbf{1}\{X_j\leq x'\})
\\=& \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},
\mathbf{1}\{X_0\leq x'\}),
\end{align*}
and $U\sim N(0,s^2)$ with 
\begin{align*}
s^2=\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,
\theta_0),h(X_j;\theta_0))
= \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),h(X_0;\theta_0)),
\end{align*}
and the covariance between $U$ and $G_{\infty}(x)$ is given by
\begin{align*}
\text{Cov}(U,G_\infty(x))=&\lim_{n\rightarrow+\infty}
\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),\mathbf{1}\{X_j\leq x\})
\\=&\sum^{+\infty}_{h=-\infty}
\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
\end{align*}
By the continuous mapping theorem, we obtain
\begin{align*}
T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|.    
\end{align*}

@@

Denote by $\mathbb{E}^{(b)}$, $\text{Var}^{(b)}$ and $\text{Cov}^{(b)}$
the expectation, variance and covariance conditional on 
$\{X_t: t = 1, \ldots, n\}$ in 
the bootstrap world. Assuming that $n=kl$ with $l$ being the block size and $k$ 
being the number of blocks, the bootstrap marginal distribution is 
\begin{align*}
\rho_n^{(b)}=\frac{1}{n}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j} \delta_{X_i},    
\end{align*}
where $\delta_x$ denotes a point mass at $x$, and $S_1,\dots,S_k$ are i.i.d 
uniform on $\{1,\dots,n-l+1\}$. 
Define $G_n^{(b)}(x)$ in the same way as $G_n(x)$ with $X_1, \dots, X_n$ being 
replaced by the bootstrap samples $X_{1:n}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.

\begin{proof}[Proof of Proposition~2]
    We want to show that
\begin{align}\label{eq-con-boot}
\begin{pmatrix}
G_n^{(b)}(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n^{(b)})-F(x;\hat{\theta}_0))
\end{pmatrix}\Rightarrow^{*}
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align}
where $\Rightarrow^*$ means convergence in distribution almost surely and 
$\hat{\theta}_0:=\mathbb{E}^{(b)}[\hat{\theta}_n^{(b)}]$. 
In the bootstrap world, we have an expansion similar to (\ref{eq-expan}):
\begin{align*}
\hat{\theta}_n^{(b)}-\hat{\theta}_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
\hat{\theta}_0) + \frac{1}{\sqrt{n}}R_n^{(b)},    
\end{align*}
where $R_n^{(b)} \overset{p^*}{\rightarrow} 0$, where 
$\overset{p^*}{\rightarrow}$ means convergence in probability almost surely. 
Note that 
\begin{align*}
\mathbb{E}^{(b)}\left[\frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
\hat{\theta}_0)\right]
=&\frac{1}{n}\sum^{k}_{j=1}\mathbb{E}^{(b)}\left[\sum^{S_j+l-1}_{i=S_j}h(X_{i};
\hat{\theta}_0)\right]
\\=&\frac{k}{n^2}[\sum^{n - l + 1}_{j=1}\sum^{j+l-1}_{i=j}h(X_{i};
\hat{\theta}_0) +
\sum^{n}_{j=n - l + 2}[\sum^{n}_{i=j}h(X_{i};\hat{\theta}_0) +
\sum^{j - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)]]
\\=&\frac{k}{n^2}\sum^{n}_{i=1}l h(X_{i};\hat{\theta}_0),
\end{align*}.
Moreover, we have
\begin{align*}
\text{var}^{(b)}\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^{(b)};
\theta_0^{(b)})\right)
=&\text{var}^{(b)}\left(\frac{1}{\sqrt{n}}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j}
h(X_{i};\hat{\theta}_0)\right)
\\=&\frac{1}{l}\text{var}^{(b)}\left(\sum^{S_1+l-1}_{i=S_1}h(X_{i};
\hat{\theta}_0)\right)
\\=&\frac{1}{ln}\sum^{n}_{t=1}(W_t-\bar{W})^2
\end{align*}
with $W_t=
 \begin{cases}
\sum^{t+l-1}_{i=t}h(X_i;\hat{\theta}_0)  & \text{if } t \leq n - 1 + 1,\\
\sum^{n}_{i=t}h(X_{i};\hat{\theta}_0) +
\sum^{t - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)  & \text{if } t \geq n - 1 + 2
\end{cases}$
and $\bar{W}=\sum^{n}_{t=1}W_t/n$,
which is expected to converge to $s^2$ almost surely. Similar calculations apply 
to $G_n^{(b)}(x)$ and we expect that
\begin{align*}
&\text{Cov}^{(b)}(G_n^{(b)}(x),G_n^{(b)}(x'))\overset{a.s.}{\rightarrow}   
\sum^{+\infty}_{h=-\infty}
\text{Cov}(\mathbf{1}\{X_{h}\leq x\},\mathbf{1}\{X_0\leq x'\}),\\
&\text{Cov}^{(b)}\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^{(b)};
\hat{\theta}_0), G_n^{(b)}(x)\right)\overset{a.s.}{\rightarrow} 
\sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
\end{align*}
By showing the finite-dimensional convergence and tightness in the bootstrap 
world (conditional on the data $\{X_t: t = 1, \ldots, n\}$), we can establish 
\eqref{eq-con-boot}.
From the CLT, the process $G_n^{(b)}(x) = \sqrt{n}(F_n^{(b)}(x) - F_n(x))$ 
converges 
to 
$G_{\infty}(x)$.

For $\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0))$, using the 
first-order Taylor 
expansion around $\hat{\theta}_0$ similarly to what was done in 
\citet{kunsch1989jackknife}, we have:
\[
F(x;\hat{\theta}_n^{(b)}) \approx F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0),
\] so
\[
\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
(F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0) - F(x;\hat{\theta}_0)) 
\approx
f(x; 
\hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0).
\]

Substituting the expansion of $\hat{\theta}_n^{(b)}$:
\[
\sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0) = \frac{1}{\sqrt{n}} 
\sum_{i=1}^{n} 
h(X_i^{(b)}; \hat{\theta}_0) + R_n^{(b)}.
\]

Since $R_n^{(b)} \overset{p^{(b)}}{\rightarrow} 0$, 
\[
\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx 
f(x; \hat{\theta}_0) \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; 
\hat{\theta}_0) \right).
\]

The term $\frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; \hat{\theta}_0)$ 
converges in distribution to a normal random variable $U$ with variance 
$s^2$.
We can show tightness of $G_n^{(b)}(x)$ similarly to how we established 
tightness of $G_n(x)$
The results then follow from the continuous mapping theorem.
\end{proof}

\bibliographystyle{plain} 
\bibliography{ref}
